Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-21 fullpaper/main.tex
update full paper

\subsubsection{Laplace Mechanism}

@@

% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$. Since $\hlg$ is monotonic, i.e. our utility function is monotonic.

% \subsubsection{Security Analysis}
% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\privinfer$. For adjacent data set $||x,y||_1 = 1$:
% \begin{equation*}
% \begin{split}
% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
% & =\frac
% {\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
% {\frac
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
% & = \left(\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp\left(\frac
% {\epsilon (u(x,r) - u(y,r))}
% {2 \Delta_{g}u}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & \leq
% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp(\epsilon).
% \end{split}
% \end{equation*}

% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

@@

\subsection{Our Approach - Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}

@@

\subsubsection{Sliding Property of Exponential Mechanism}
\begin{lem}
Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

\subsubsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

>>>>

@@

@@

\subsubsection{Laplace Mechanism}
\begin{itemize}
  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$.
  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$.
  % \item \todo{$S\propto ||\cdot ||_{1}$}.
  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$.
  \end{itemize}

\subsubsection{Improved Baseline Approach}

y using sensitivity 1 in 2 dimensions and 2 in higher dimensions.
    Indeed: we can see the output of the Bayesian inference as a histogram, and $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.

\subsection{Our approach: smoothed Hellinger distance based exponential mechanism}
\label{sec_smoo}

@@

\subsubsection{Sliding Property of $\hexpmech$}
\begin{lem}
Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

\subsubsection{Dilation Property of $\hexpmech$}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:
